Figures and Tables

### 2021-02-02 paper/figures_tables.Rmd
Updates to figures and captions in 4.

## Seed dispersal distances and aggregation

```{r fig.width=6}
bind_rows(null_dispersal %>% mutate(model = "Null"), 
          indiv_dispersal %>% mutate(model = "Individual"),
          fam_dispersal %>% mutate(model = "Family")) %>% 
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> dispersal_data

@@

null_dispersion %>% 
  mutate(model = "Null") %>% 
  bind_rows(indiv_dispersion %>% 
              mutate(model = "Individual")) %>% 
  bind_rows(fam_dispersion %>% 
              mutate(model = "Family")) %>% 
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> all_disp_data

all_disp_data %>% 
  ggplot(., aes(y = mean_xy_dispersal, x = model)) +
  geom_boxplot() +
  theme_bw() +
  labs(y = "Mean dispersal (m)") +
  theme(axis.title.x = element_blank()) -> a

@@

boxplots <- plot_grid(a,b, ncol = 2, align = "h", labels = c("b", "c"))

plot_grid(histograms, boxplots, nrow=2, labels = c("a", ""))

>>>>

## Seed dispersal distances and aggregation
#### Figure 4. Seed dispersal distances and aggregation metrics for simulated seeds in the three models considering variation in animal movement rates. **A.** Density kernels for frugivore-generated seed dispersal distances for each seed simulated under the three models of variation in animal movement rates. Each individual line represents the dispersal kernel generated by each individual animal. The null model assumes the same movement rate for all animals, whereas individual and family models use a movement rate for each animal id, or family group. **B.** Box plot comparing the distances from the parent tree at the origin to the mean seed location in each simulation run among the three simulation models. **C.** Box plot comparing the seed aggregation metric, seed dispersion, for each simulation run between the three simulation models. *Is there more comparison I should mention here? Like, how the larger values are more abundant in the individual model?*

```{r fig.width=6}

# Dispersal data for each of the seeds
bind_rows(null_dispersal %>% mutate(model = "Null"), 
          indiv_dispersal %>% mutate(model = "Individual"),
          fam_dispersal %>% mutate(model = "Family")) %>% 
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> dispersal_data

@@

dispersal_data %>% 
  ggplot(., aes(x = dispersal, group = id)) +
  facet_wrap(~model, ncol = 3) +
  geom_density() +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white")) +
  labs(y = "Density", x = "Seed dispersal (m)") -> histograms_by_id

# These measures are by simulation run. So, they are average/mean seed dispersal and seed dispersion. Only one value per simulation run.  
null_dispersion %>% 
  mutate(model = "Null") %>% 
  bind_rows(indiv_dispersion %>% 
              mutate(model = "Individual")) %>% 
  bind_rows(fam_dispersion %>% 
              mutate(model = "Family")) %>% 
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> all_disp_data

all_disp_data %>% 
  ggplot(., aes(y = mean_xy_dispersal, x = model)) +
  geom_boxplot() +
  theme_bw() +
  labs(y = "Average seed location (m)") +
  theme(axis.title.x = element_blank()) -> a

@@

boxplots <- plot_grid(a,b, ncol = 2, align = "h", labels = c("B", "C"))

plot_grid(histograms_by_id, boxplots, nrow=2, labels = c("A", ""))
